\section{Related Work}
\label{sec:rw}
\meddle builds upon two existing technologies: VPNs and middleboxes. 
In our current implementation, we rely on an IPsec~\cite{rfc:ipsec} implementation 
to tunnel traffic to \meddle servers. Sekar et al.~\cite{sekar:middleboxes} investigated consolidating middleboxes 
to reduce costs and improve load balance. Sherry et al.~\cite{sherry:middleboxes} explore the opportunities 
enabled by moving middleboxes to the cloud, which includes simplifying management 
for enterprise network administrators. In contrast, our work focuses on the mobile capabilities 
that software middleboxes enable rather than a redirection architecture for enterprise networks. 

\meddle provides researchers with a cross-platform, cross-carrier technique 
for capturing network usage patterns from mobile devices. Previous work 
used on-demand active measurements to characterize performance~\cite{wang:middleboxes,speedtest}; 
however, these measurements are restricted to the point at which users run 
the tests. Gerber et al.~\cite{gerber:passivespeed} use passive measurements alone 
to estimate transfer rates in a single carrier's network; \meddle 
enables such analysis across multiple carriers.

We use \meddle to investigate security and privacy issues in the 
traffic that mobile devices generate. By monitoring and controlling 
information at lower layers in the software stack, previous work~\cite{enck:taintdroid,hornyack:appfence,wsj:apps-watching-you} has shown 
that existing apps leak significant private information. In \meddle, we take 
this downward mobility to an extreme, moving off the end-host entirely and 
eliminating the restrictions of a lab setting. We demonstrated that  
many identifiers are being leaked in the clear, which our approach can 
block or modify without needing any additional support (\eg, taint tracking) 
from the operating system. We are investigating 
opportunities for detecting information leakage when apps use encrypted 
channels and/or obfuscation.

\meddle allows us to improve data and energy consumption by blocking 
unsolicited content such as advertisements, and by blocking unwanted 
traffic during idle periods. Vallina-Rodriguez et al.~\cite{vallina-rod:ads} demonstrated 
that ads account for a significant portion of data consumption. Pathak et al.~\cite{pathak:eprof} 
showed that ads can consume a significant fraction of an app's overall energy consumption. 
Importantly, \meddle not only allows us to characterize unsolicited content, but 
also allows us to block it without OS or app modification.

The CloneCloud~\cite{chun:clonecloud} and MAUI~\cite{cuervo:maui} projects explored the space of moving functionality 
from mobile devices into the cloud. By interposing on user traffic, \meddle will allow us to explore some of this 
functionality without requiring device modifications.


%** User Behavior and Energy consumption
%  - Falling Asleep Angry Birds -- Appsensor MobileHCI'12 
%     - Meddle is passive
%  - Who killed my battery - WWW'12 
%** Web caching 
%  - ATT papers - periodic nature stuff