\subsection*{Abstract}

We present, Meddle, a platform that relies on traffic indirection to diagnose mobile Internet traffic.
Meddle is motivated by the absence of built-in support from ISPs and mobile OSes to freely monitor and control mobile Internet traffic; the restrictions imposed by mobile OSes and ISPs also make existing approaches impractical.
%Instrumenting mobile OSes, static and dynamic analysis of application binaries, or the privilege of working with ISPs---impractical. 
Meddle overcomes these hurdles by relying on the native support for traffic indirection by mobile OSes.
Specifically, Meddle proxies mobile Internet traffic through a software defined middleboxes configured for mobile traffic diagnosis. 
In this paper, we use Meddle to tests the limits of the network perspective of mobile Internet traffic offered by traffic indirection. 

We use this perspective to characterize and control the behavior of mobile applications and provide a first look at ISP interference on mobile Internet traffic. 
We then performed controlled experiments on 100 popular iOS and Android applications to show how Meddle can be used to identify misbehavior and to block traffic causing this misbehavior. 
Unlike existing solutions, this activity can be performed without warranty voiding the device and activated on the fly on-demand. 
\tbd{We also report on how ISP interfere with mobile HTTP Internet traffic.}








%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "meddle-main"
%%% End: 
