\section{ALL PLACHOLDER SECTIONS COME HERE}

\input{placeholder-tex/dataset}

%\input{placeholder-tex/methodology}

\input{placeholder-tex/measurements}

\input{placeholder-tex/related}

Bro port based classification of HTTP, SSL, other, and so on. 


\section{Classification of Application}

\platname enables us to monitor the data being exchanged by the mobile device. 
However, it does not provide any details of the source of the data. 
We use the following technique to estimate the source of the mobile data traffic. 
In \ref{tab:summaryIOSAndroidTraffic} and \ref{tab:summaryWifiCellularTraffic} we observe that TCP is responsible for the majority of the traffic volume from iOS and Android devices regardless of the access technology used. 
We therefore focus on associating TCP flows to the applications for our analysis. 
From our analysis we were able to classify \tbdv{x\%} of the TCP traffic volume and \tbdv{y\%} of the TCP flows to the applications.

\subsection{Methodology}

\subsection{Results}

User Agent based classification
flows per user with a blank user agent. 
flows per user with a default user agent 
flows with application in user agent


SSL certificate based classification
flows to dedicated hosts
flows to cdns

\subsection{Discussion}

\section{Specific application behavior}


\section{Ads and Analytics}

Ads and Analytic sites have received considerable attention.
The reason for the attention being the intrusiveness exhibited by the ads and analytics sites in tracking personal information. 
\cite{vallina-rod:ads} show that \tbdv{ } of data traffic volume observed from a Cellular ISP is because of mobile ads. 
In our traces we use the classification of \cite{vallina-rod:ads} and \cite{YoyoAds} to classify flows as ads flows. 



\section{Discussion on Platform}

IPv6 support of VPNs

ISP support of VPNs. One ISP blocked VPN access. 

Open source ??

Releasing datasets ??


