%\vspace{-0.7em}
\section{Related Work}

\meddle builds upon two existing technologies: VPNs and middleboxes. 
In our current implementation, we rely on an IPsec~\cite{rfc:ipsec} implementation 
to tunnel traffics to \meddle servers. Sherry et al.~\cite{sherry:middleboxes} explore the opportunities 
enabled by moving middleboxes to the cloud, which includes simplifying management 
for enterprise network administrators. In contrast, our work focuses on the mobile capabilities 
software middleboxes enable rather than a redirection architecture for enterprise networks. 

\meddle provides researchers with a cross-platform, cross-carrier technique 
for capturing network usage patterns from mobile devices. Previous work 
used on-demand active measurements to characterize network measurements~\cite{wang:middleboxes,speedtest}; 
however, these measurements are restricted to the point at which users run 
the tests. Gerber et al.~\cite{gerber:passivespeed} use passive measurements alone 
to estimate transfer rates in a single carrier's network; \meddle 
will enable such analysis across multiple carriers.

We expect to use \meddle to investigate security and privacy issues in the 
traffic that mobile devices generate. By monitoring and controlling 
information at lower layers in the software stack, previous work~\cite{enck:taintdroid,hornyack:appfence,wsj:apps-watching-you} has shown 
that existing apps leak significant private information. In \meddle, we take 
this downward mobility to an extreme, moving off the end-host entirely and 
eliminating the restrictions of a lab setting.

The CloneCloud~\cite{chun:clonecloud} and MAUI~\cite{cuervo:maui} projects explored the space of moving functionality 
from mobile devices into the cloud. By interposing on user traffic, \meddle will allow us to explore some of this 
functionality without requiring device modifications.

%\vspace{-0.7em}
\section{Conclusion}
We described \meddle, a platform for users to regain control of their mobile 
network traffic while giving researchers a foothold to deploy new mobile network 
services and to characterize usage behaviors in the wild. We showed that the overheads 
for \meddle are low and that \meddle can easily scale to thousands of users. We are currently using our  
prototype \meddle architecture to build out a system for public deployment.
%In this work, we described an approach we call \meddle that empowers users and researchers with new 
%control over mobile network traffic. We used network and power measurements to 
%demonstrate that the overhead of using \meddle for mobile devices is relatively low, and that 
%our approach should scale reasonably well in terms of supporting thousands of users with 
%a collection of PlanetLab hosts and/or EC2 instances. Our future work entails using 
%this platform to experiment with alternative performance-enhancing interposition techniques, 
%to explore the limits of how much control we can enforce with middleboxes and 
%to investigate how to combine functionality from on-device apps with \meddle to 
%provide new mobile network measurements and services.

%%% Local Variables: 
%%% TeX-master: "hotnets-meddle-middle.tex"
%%% End:
