\section{Motivation}

What is the problem we are targetting?
Lack of transparency and control in what?

Why is this problem important? 

\subsection{Lack of Transparency and Control} 

What do we mean by transparency and control? 
Why is it important?
What is the scope of transparency? 
What is the scope of control?
Transparency includes awareness on \emph{what} our mobile devices do with our information, with \emph{whom} our mobile devices communicate, and \emph{how} our mobile devices interact with other devices on the Internet and the impact of such interaction.
Transparency enables the auditing.
Control empowers us with the authority to exert our influence on how our devices participate in the mobile ecosystem

Why is there a lack of transparency and control?
OSes require control to isolate applications and determine set of OS level services to maximize resource availability -- battery life, data quotas etc. 
Vested interests backed by commercial agreements -- preinstalled applications that cannot be removed point to commercial services of ISPs, creators of OS etc. For example, Deezer installed on Orange phones, Google Play on Android device. 
Advertisement based revenue model encourages opaqueness on how user profiles are built based on privacy leaks. 

To whom is this problem interesting?

Why should the reader be interested?


\subsection{Discussion on Existing solutions}

\subsubsection{Instrumenting OSes}

Taintdroid \cite{enck:taintdroid}.
AppFence \cite{hornyack:appfence}.
Eprof \cite{pathak:eprof}.
ProfileDroid \cite{wei:profiledroid}.
mobile Application Resource Optimizer(ARO)~\cite{qian:mobilearo}.
Behavior of applications dependent on APIs provided by OSes. 
Applications can therefore behave differently 
Does not cover new OSes.
Violates terms and conditions making it impractical for end-users. 

\subsubsection{Instrumenting Applications}
PIOS \cite{egele:pios}.
AppInsight \cite{ravindranath:appinsight}
Limited applications.
Does not consider application updates. 
Requires connections to specific stores with limited number of applications. 

\subsubsection{Logging Application Behavior}
\cite{falaki:smartphoneusage}

\subsubsection{Traffic Logs From ISPs and Wi-Fi Gateways}
Limited network coverage. 
Restricted to specific ISPs and access technologies. 
Region specific applications are not covered. 


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "meddle-main"
%%% End: 
